Make any stupid plot you want

### 2021-02-24 draft/sections/math.tex
pulled up jet to definition of artist since thats when is needed

\subsubsection{Sheaf and Stalk}
\label{sec:data_sheaf_stalk}
The section \dsection\ is defined globally on \dbase, including infinite \dbase\ for streaming data and total \dbase\ for chunked data, but often we want as input into the artist \vartist\ a subset of the data. For example sliding window\cite{crouchDynamicGraphsSlidingwindow2013,chuTimeSeriesSegmentation1995} based visualizations of streaming data, or visualizations that support pan and zoom navigation\cite{NekrasovskiEvaluationPanZoom2006}. To make these types of visualizations, mathematical objects called sheafs provide a way to construct a \dsection\ on a subset of \dbase.

Another use for the sheaf is to provide access to all the records over the space on which the sheaf $\mathcal{O}(\dtotal)$ is defined. The artist \vartist\ could not generate any visualization that needed more information than was in a single record, such as a line plot, if it took as input \dsection, because $\dsection:\dbasepoint \mapsto \delement$ only knows about the record it returns. While taking  $\mathcal{O}(\dtotal)$ as input would solve this issue, in practice, often the only information \vartist\ needs is some finite number $n$ of derivatives, which is captured by the jet bundle $\mathcal{J}^n$ \cite{JetBundle2020,musilovaCalculusVariationsJet2016} with $\mathcal{J}^{0}(\dtotal)=\dtotal$. In this work, we at most need $\mathcal{J}^{2}(\dtotal)$ which is the value at \dsection\ and its first and second derivatives. The sheaf facilitates interactions such as zooming or updating the graphic based on zooming data; the jet ensures that the artist only needs a single record on \dbasepoint\ extended with derivatives to render a piece of a graphic. This allows for the creation of highly concurrent and possibly distributed artists.

@@

The artist is the function that converts data into graphics; its name is taken from the analogous part of Matplotlib\cite{hunterArchitectureOpenSource} that builds visual elements to pass off to the renderer. The artist \vartist\ is a mapping from \dtotal\ padded with data from $\dtotal^{\prime}=\mathcal{J}(\dtotal)$ to a graphic that is a section $\gsection \in \Gamma(\gtotal)$

\begin{equation}
    \label{eq:artist_diagram}
    \begin{tikzcd}
        \dtotal^{\prime} \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] & \gtotal \arrow[ld, "\pi"] \\
                                              & \dbase                  & \gbase \arrow[l, "\vindex"']                                              &                    
        \end{tikzcd}
\end{equation}

which due to using the jet is point wise such that the input can be $\dsection(\dbasepoint)$. The encoders $\vchannel:\dtotal^{\prime} \rightarrow \vtotal$ converts the data components to visual components(\ref{sec:graphic_base}). The continuity map $\vindex:\gbase \dbase$ then pulls back the visual bundle \vtotal\ over \gbase (\ref{sec:artist_nu}). Then the assembly function $\vmark: \vtotalpull \rightarrow \gtotal$ composites the fiber components of \vtotalpull\ into a graphic in \gtotal (\ref{sec:artist_q}). This functional decomposition of the visualization artists allows us to specify what are the responsibilities of each function in a fully constrained way. In turn, this allows for building reusable components at each stage of the transformation.

@@

>>>>

@@

The artist is the function that converts data into graphics; its name is taken from the analogous part of Matplotlib\cite{hunterArchitectureOpenSource} that builds visual elements to pass off to the renderer. The topological artist \vartist\  is a monoid equivariant sheaf map from the sheaf on a data bundle \dtotal\ which is $\mathcal{O}(\dtotal)$ to the sheaf on the graphic bundle \gtotal, $\mathcal{O}(\gtotal)$. 
\begin{equation}
    \vartist: \mathcal{O}(\dtotal) \rightarrow \mathcal{O}(\gtotal)
\end{equation}

Usually \vartist can usually map into graphical elements solely with the data in \dsection, some visualizations, such as line, may also need some finite number $n$ of derivatives, which is captured by the jet bundle $\mathcal{J}^n$ \cite{JetBundle2020,musilovaCalculusVariationsJet2016} with $\mathcal{J}^{0}(\dtotal)=\dtotal$. In this work, we at most need $\mathcal{J}^{2}(\dtotal)$ which is the value at \dsection\ and its first and second derivatives; therefore the artist takes as input the data bundle padded with the jet bundle $\dtotal^{\prime} = \dtotal + \mathcal{J}^{2}(\dtotal)$. Specifically, \vartist is the map from $\dtotal^{\prime}$ to a specific graphic $\gsection \in \Gamma(H)$

\begin{equation}
    \label{eq:artist_diagram}
    \begin{tikzcd}
        \dtotal^{\prime} \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] & \gtotal \arrow[ld, "\pi"] \\
                                              & \dbase                  & \gbase \arrow[l, "\vindex"']                                              &                    
        \end{tikzcd}
\end{equation}
where the input can be point wise $\dsecton(\dbasepoint)\mid \dbasepoint \in \dbase$. The encoders $\vchannel:\dtotal^{\prime} \rightarrow \vtotal$ convert the data components to visual components(\ref{sec:graphic_base}). The continuity map $\vindex:\gbase \rightarrow \dbase$ then pulls back the visual bundle \vtotal\ over \gbase (\ref{sec:artist_nu}). Then the assembly function $\vmark: \vtotalpull \rightarrow \gtotal$ composites the fiber components of \vtotalpull\ into a graphic in \gtotal (\ref{sec:artist_q}). This functional decomposition of the visualization artists allows us to specify what are the responsibilities of each function in a fully constrained way. In turn, this allows for building reusable components at each stage of the transformation.

@@

\subsubsection{Sheaf and Stalk}
\label{sec:data_sheaf_stalk}
\note{move to artost}
Another use for the sheaf is to provide access to all the records over the space on which the sheaf $\mathcal{O}(\dtotal)$ is defined. The artist \vartist\ could not generate any visualization that needed more information than was in a single record, such as a line plot, if it took as input \dsection, because $\dsection:\dbasepoint \mapsto \delement$ only knows about the record it returns. 
The data bundle \dtotal\ is defined globally on \dbase, but often we want as

 To make these types of visualizations, mathematical objects called sheafs provide a way to construct a \dsection\ on a subset of \dbase.

The sheaf facilitates visualizations such as sliding windows\cite{crouchDynamicGraphsSlidingwindow2013,chuTimeSeriesSegmentation1995} streaming data, or navigation such as pan and zoom\cite{NekrasovskiEvaluationPanZoom2006}.; the jet ensures that the artist only needs a single record on \dbasepoint\ extended with derivatives to render a piece of a graphic. This allows for the creation of highly concurrent and possibly distributed artists.
